---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# glossary

<!-- badges: start -->
<!-- badges: end -->

The goal of glossary is to provide a lightweight solution for making glossaries in educational materials written in quarto or R Markdown.

## Installation

You can install the development version of glossary from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("debruine/glossary")
```

## Quick Start

### Setup

```{r}
library(glossary)
```

### Definition File

Set the default path to the definition file.

```{r}
glossary_path("inst/glossary.yml")
```

You can store definitions in a YAML file like this:

```
alpha: |
  The threshold chosen in Neyman-Pearson hypothesis testing to distinguish test results that lead to the decision to reject the null hypothesis, or not, based on the desired upper bound of the Type 1 error rate. An alpha level of 5% it most commonly used, but other alpha levels can be used as long as they are determined and preregistered by the researcher before the data is analyzed.
p-value: |
  The probability of the observed data, or more extreme data, if the null hypothesis is true. The lower the p-value, the higher the test statistic, and less likely it is to observe the data if the null hypothesis is true.
```

### Style

Set a glossary entry style like this at the top of your document (set the code chunk to `results='asis'`).

```{r, results='asis'}
glossary_style(color = "green", text_decoration = "purple underline")
```

### In-Text Terms

Hover over the highlighted terms to see the definition.

Look up a term from the glossary file with `glossary("alpha")`: `r glossary("alpha")`

Display a different value for the term with `glossary("alpha", "$\\alpha$")`: `r glossary("alpha", "$\\alpha$")`

Use an inline definition instead of the glossary file with `glossary("beta", def = "The second letter of the Greek alphabet")`: `r glossary("beta", def = "The second letter of the Greek alphabet")`

Just show the definition with `glossary("p-value", show_def = TRUE)`: `r glossary("p-value", show_def = TRUE)`

### Glossary Table

Show the table of terms defined on this page with `glossary_table()`:

```{r, echo = FALSE}
glossary_table()
```

Reset the glossary table between sections with `glossary_reset()`.


