---
title: "glossary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{glossary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

```{r setup}
library(glossary)
```


## Definition File

Set the default path to the definition file.

```{r}
glossary_path("glossary.yml")
```

You can store definitions in a YAML file like this:

```
SESOI: |-
  Smallest Effect Size of Interest: the smallest effect that is theoretically or practically meaningful

  See [Equivalence Testing for Psychological Research](https://doi.org/10.1177/2515245918770963) for a tutorial on methods for choosing an SESOI.
p-value: |-
  The probability of the observed data, or more extreme data, if the null hypothesis is true. The lower the p-value, the higher the test statistic, and less likely it is to observe the data if the null hypothesis is true.
```

Alternatively, you can add definitions to the file with code.

```{r, eval = FALSE}
glossary_add(term = "power",
             def = "The probability of rejecting the null hypothesis when it is false, for a specific analysis, effect size, sample size, and criteria for significance."
")
```


## Style

By default, the in-text glossary terms will be styled like other links in your document. You can set a different style at the top of your document (set the code chunk to `results='asis'`).

```{r, results='asis'}
glossary_style(color = "green", text_decoration = "purple underline")
```

Alternatively, you can add your own CSS to your document to create a more customised appearance.

```{css}
<style>
a.glossary {
  color: green;
  text-decoration: purple underline;
  cursor: help;
}
</style>
```

## In-Text Terms

Hover over the highlighted terms to see the definition.

* Look up a term from the glossary file with `glossary("alpha")`: `r glossary("alpha")`

* Display a different value for the term with `glossary("alpha", "$\\alpha$")`: `r glossary("alpha", "$\\alpha$")`

* Use an inline definition instead of the glossary file with `glossary("beta", def = "The second letter of the Greek alphabet")`: `r glossary("beta", def = "The second letter of the Greek alphabet")`

* Just show the term (no hover) with `glossary("effect size", show = "term")`: `r glossary("effect size", show = "term")`

* Just show the definition with `glossary("p-value", show = "def")`: `r glossary("p-value", show = "def")`

## Glossary Table

Show the table of terms defined on this page (or since the last reset) with `glossary_table()`:

```{r, echo = FALSE}
glossary_table()
```

You can reset the glossary table between sections with `glossary_reset()`.



